---
title: "Response of Pinguicula vulgaris to geothermal heating"
subtitle: "Data preparation"
author : "Alicia Valdés"
output:
  pdf_document:
    latex_engine: xelatex
    toc: yes
    toc_depth: 4
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
options(tibble.width = Inf)
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

```{r load packages, include=FALSE}
library(tidyverse)
library(readxl)
library(lubridate)
```

# Read data from Excel files

```{r}
ping_17 <- read_excel("data/raw/Hengill 2017.xlsx", sheet = "Pinguicula")
ping_18 <- read_excel("data/edited/Hengill 2018_AV.xlsx", 
                      sheet = "Pinguicula_AV")
ping_20 <- read_excel("data/edited/Hengill 2020_AV.xlsx",
                      sheet = "Pinguicula_AV")
ping_17_peak <- read_excel("data/raw/Hengill 2017.xlsx", 
                           sheet = "Peak Pinguicula")
ping_18_peak <- read_excel("data/raw/Hengill 2018.xlsx", 
                           sheet = "Peak Pinguicula")
ping_20_peak <- read_excel("data/edited/Hengill 2020_AV.xlsx", 
                           sheet = "Peak Pinguicula_AV")
ping_17_seeds <- read_excel("data/raw/Iceland_seedscount_sowing_2017_Malin.xlsx",
                            sheet = "Pinguicula")
ping_17_seedpods <- read_excel("data/raw/2017_Seedpodcounts+collections.xlsx",
                            sheet = "Pinguicula")
ping_18_seeds <- read_excel("data/raw/2018_Seedcounts+collections.xlsx",
                            sheet = "Pinguicula")
```

# Remove rows with all NAs

```{r}
ping_17 <- ping_17 %>% drop_na(X:Y) %>% # Removing one row with all NAs
  filter(X!="X") # Removing one row with all NAs written as "X"
```

```{r}
ping_18 <- ping_18 %>% drop_na(X:Y) %>% # Removing one row with all NAs
  filter(X!="X") # Removing one row with all NAs written as "X"
```

```{r}
ping_20 <- ping_20 %>% drop_na(X:Y) # Removing one row with all NAs
```

# Change column types

```{r}
ping_17 <- ping_17 %>% mutate(plot=as.factor(Plot),id=Indv,
                              x=as.numeric(X),y=as.numeric(Y),
                              peak=as.factor(ifelse(Peak=="X",1,0)),
                              comments=Comments,
                              date1=as.Date(Date...7,format="%d.%m.%y"),
                              temp=as.numeric(Temp),stage1=Stage...9,
                              date2=as.Date(Date...10,format="%d.%m.%y"),
                              stage2=Stage...11,
                              date3=as.Date(Date...12,format="%d.%m.%y"),
                              stage3=Stage...13,
                              date4=as.Date(Date...14,format="%d.%m.%y"),
                              stage4=Stage...15,
                              date5=as.Date(Date...16,format="%d.%m.%y"),
                              stage5=Stage...17,
                              date6=as.Date(Date...18,format="%d.%m.%y"),
                              stage6=Stage...19) %>%
  dplyr::select(-(Plot:Stage...19))
```

```{r}
ping_18 <- ping_18 %>% mutate(plot=as.factor(Plot),id=Indv,
                              x=as.numeric(X),y=as.numeric(Y),
                              peak=as.factor(ifelse(Peak=="-",0,1)),
                              comments=Comments,
                              date1=as.Date(Date...7,format="%d.%m.%y"),
                              temp1=as.numeric(Temp...8),stage1=Stage...9,
                              date2=as.Date(Date...10,format="%d.%m.%y"),
                              stage2=Stage...11,
                              date3=as.Date(Date...12,format="%d.%m.%y"),
                              stage3=Stage...13,
                              date4=as.Date(Date...14,format="%d.%m.%y"),
                              stage4=Stage...15,
                              date5=as.Date(Date...16,format="%d.%m.%y"),
                              stage5=Stage...17,
                              date6=as.Date(Date...18,format="%d.%m.%y"),
                              stage6=Stage...19,
                              date7=as.Date(Date...20,format="%d.%m.%y"),
                              stage7=Stage...21,
                              date8=as.Date(Date...22,format="%d.%m.%y"),
                              stage8=Stage...23,
                              date9=as.Date(Date...24,format="%d.%m.%y"),
                              temp2=as.numeric(Temp...25)) %>%
  dplyr::select(-(Plot:Temp...25)) %>%
  filter(stage1!="X"&stage2!="X") %>% # Removing rows with all stages as "X"
  mutate(temp1=ifelse(temp1>80,8.7,temp1)) # Correct error in temp1
# Temperature measured two times, at the beginning and end of the season
# (temp1 and temp2) --> calculate temp
ping_18 <- ping_18 %>% 
  mutate(temp=ifelse(is.na(temp1),temp2, # usetemp2 when temp1 is NA
                     ifelse(is.na(temp2),temp1, # use temp1 when temp2 is NA
                            (temp1+temp2)/2))) %>% # otherwise use mean
  dplyr::select(-temp1) %>% # Remove columns
  dplyr::select(-(date9:temp2))
```

```{r}
ping_20 <- ping_20 %>% 
  mutate(plot=as.factor(Plot),id=`# 2020`,x=as.numeric(X),y=as.numeric(Y),
         peak=ifelse(`Peak/Aborted/Stem gone`=="-",0,1),
         comments=Comments,
         start_treatment=as.Date(`Start of treatment`,format="%d.%m.%y"),
         treatment=as.factor(ifelse(Treatment=="0",NA,Treatment)),
         date1=as.Date(`Week 3`,format="%d.%m.%y"),stage1=Stage...10,
         temp1=as.numeric(`°C Preliminary 2020`),
         date2=as.Date(`Week 4`,format="%d.%m.%y"),stage2=Stage...13,
         date3=as.Date(`Week 5`,format="%d.%m.%y"),stage3=Stage...15,
         date4=as.Date(`Week 6`,format="%d.%m.%y"),stage4=Stage...17,
         date5=as.Date(`Week 7`,format="%d/%m/%y"),stage5=Stage...19,
         temp2=as.numeric(`Temp 1`),
         date6=as.Date(`Week 8`,format="%d/%m/%y"),stage6=Stage...22,
         date7=as.Date(`Week 9`,format="%d/%m/%y"),stage7=Stage...24,
         date8=as.Date(`Week 10`,format="%d/%m/%y"),stage8=Stage...26,
         date9=as.Date(`Week 11`,format="%d.%m.%y"),stage9=Stage...28,
         date10=as.Date(`Week 12`,format="%d/%m/%y"),stage10=Stage...30,
         date11=as.Date(`Week 13`,format="%d/%m/%y"),
         temp3=as.numeric(`Temp 2`),stage11=Stage...33,
         date12=as.Date(`Weel 14`,format="%d/%m/%y"),stage12=Stage...35,
         date13=as.Date(`Week 15`,format="%d/%m/%y"),stage13=Stage...37,
         date14=as.Date(`Week 16`,format="%d.%m.%y"),stage14=Stage...39) %>%
  dplyr::select(-(Plot:Stage...39)) %>%
  mutate(temp=ifelse(is.na(temp2)&is.na(temp3),temp1,
                     ifelse(is.na(temp1),(temp2+temp3)/2,
                            ifelse(is.na(temp2),(temp1+temp3)/2,
                                   (temp1+temp2)/2)))) %>% 
  dplyr::select(-temp1) %>% # Remove columns
  dplyr::select(-temp2) %>%
  dplyr::select(-temp3) %>%
  # Two plants that have peak=1, but in reality peak=0
  mutate(peak=ifelse(id=="P-224"|id=="P-225",0,peak)) %>%
  mutate(peak=as.factor(peak))
```

# Convert to long format and divide stage into real stage + grazing

"stage" column contains info on stage:

-   V (Vegetative) Only vegetative growth, the plant only has leaves
-   B1 (Bud stage 1) Buds are just starting to form, very small, close to leaves
-   B2 (Bud stage 2) Buds are at medium size
-   B3 (Bud stage 3) Buds are large but still completely closed
-   B4 (Bud stage 4) Buds are large and starting to open
-   FL (Flowering) At least one flower has opened
-   FL100 (100% flowering) All flowers have opened, none are yet wilted
-   W (Wilted) At least one flower has wilted
-   W100 (100% wilted) All flowers have wilted

But also on grazing / lost and dead plants:

-   X (Lost) Neither plant nor nail was not found that day

-   D (Dead) Plant still in place but dead

-   G (Grazed/gone) Nail was found but no sign of plant

-   SG (Stem grazed/gone) All stems grazed/gone but with visible stubs

-   /G (Grazing damage) One or more stems have been grazed but there are still some left, phenology is measured for the one that is most mature

Separate info from "stage" column into "stage" and "graz" columns. Remove plants that did not flower (where there is no record with stages FL or FL100 or W or W100). 

```{r}
ping_17_long <- full_join(
  ping_17 %>% 
    pivot_longer(cols=starts_with("date"),names_to="revision",
                 names_prefix="date",values_to="date") %>%
    dplyr::select(plot,id,x,y,comments,temp,revision,date),
  ping_17 %>% 
    pivot_longer(cols=starts_with("stage"),names_to="revision",
                 names_prefix="stage",values_to="stage") %>%
    dplyr::select(plot,id,x,y,comments,temp,revision,stage)
  ) %>%
  separate(stage,into=c("stage","graz"),sep="/") %>%
  mutate(stage=ifelse(stage=="FL50","FL",ifelse(stage=="GL","FL",stage))) 
# One record with stage=FL50 --> changed to stage=FL
# One record with stage="GL" - I suppose it is "FL" --> changed to this

nrow(ping_17_long%>%distinct(id)) # 405 ids

ids_fl_17 <- filter(ping_17_long, stage %in% c("FL","FL100","W","W100"))%>%
  distinct(id) 
nrow(ids_fl_17) # 292 ids that flowered
  
ping_17_long <- ping_17_long %>%
  filter(id %in% as.vector(ids_fl_17$id))

length(unique(ping_17_long$id)) # Now including only the 292 ids that flowered

ping_17_long$graz <- with(ping_17_long,
                          ifelse(stage %in% c("SG","D","G","X"),
                            stage,graz)) # Info that should be on "graz" column
ping_17_long$stage  <- with(ping_17_long,
                          ifelse(stage %in% c("SG","D","G","X"),
                            NA,stage))

unique(ping_17_long$stage) # Now correct info on "stage"
unique(ping_17_long$graz) # and on "graz"
```
```{r}
ping_18_long <- full_join(
  ping_18 %>% 
    pivot_longer(cols=starts_with("date"),names_to="revision",
                 names_prefix="date",values_to="date") %>%
    dplyr::select(plot,id,x,y,comments,temp,revision,date),
  ping_18 %>% 
    pivot_longer(cols=starts_with("stage"),names_to="revision",
                 names_prefix="stage",values_to="stage") %>%
    dplyr::select(plot,id,x,y,comments,temp,revision,stage)
  ) %>%
  mutate(stage=ifelse(stage=="N/A",NA,stage)) %>%
# One record with stage=N/A --> changed to stage=NA
  separate(stage,into=c("stage","graz"),sep="/")
  
nrow(ping_18_long%>%distinct(id)) # 373 ids

ids_fl_18 <- filter(ping_18_long, stage %in% c("FL","FL100","W","W100"))%>%
  distinct(id) 
nrow(ids_fl_18) # 201 ids that flowered
  
ping_18_long <- ping_18_long %>%
  filter(id %in% as.vector(ids_fl_18$id))

length(unique(ping_18_long$id)) # Now including only the 201 ids that flowered

ping_18_long$graz <- with(ping_18_long,
                          ifelse(stage %in% c("SG","D","G","X"),
                            stage,graz)) # Info that should be on "graz" column
ping_18_long$stage  <- with(ping_18_long,
                          ifelse(stage %in% c("SG","D","G","X"),
                            NA,stage))

unique(ping_18_long$stage) # Now correct info on "stage"
unique(ping_18_long$graz) # and on "graz"
```
```{r}
ping_20_long <- full_join(
  ping_20 %>% 
    pivot_longer(cols=starts_with("date"),names_to="revision",
                 names_prefix="date",values_to="date") %>%
    dplyr::select(plot,id,x,y,comments,temp,revision,date),
  ping_20 %>% 
    pivot_longer(cols=starts_with("stage"),names_to="revision",
                 names_prefix="stage",values_to="stage") %>%
    dplyr::select(plot,id,x,y,comments,temp,revision,stage)
  ) %>%
  # Make stages similar to previous years
  mutate(stage=ifelse(stage=="F","FL",stage)) %>%
  mutate(stage=ifelse(stage=="F1/1","FL100",stage)) %>%
  mutate(stage=ifelse(stage=="F/1/1","FL100",stage)) %>%
  mutate(stage=ifelse(stage=="F1/2","FL",stage)) %>%
  mutate(stage=ifelse(stage=="F1/1/SG","FL100/SG",stage)) %>%
  mutate(stage=ifelse(stage=="F2/2","FL100",stage)) %>%
  mutate(stage=ifelse(stage=="F2/3","FL",stage)) %>%
  mutate(stage=ifelse(stage=="F1/1/","FL100",stage)) %>%
  mutate(stage=ifelse(stage=="F1/3","FL",stage)) %>%
  mutate(stage=ifelse(stage=="W00","W100",stage)) %>% # Correct error
  mutate(stage=ifelse(stage=="S100","W100",stage)) %>% # Correct error
  separate(stage,into=c("stage","graz"),sep="/")
  
nrow(ping_20_long%>%distinct(id)) # 450 ids

ids_fl_20 <- filter(ping_20_long, stage %in% c("FL","FL100","W","W100"))%>%
  distinct(id) 
nrow(ids_fl_20) # 287 ids that flowered
  
ping_20_long <- ping_20_long %>%
  filter(id %in% as.vector(ids_fl_20$id))

length(unique(ping_20_long$id)) # Now including only the 287 ids that flowered

ping_20_long$graz <- with(ping_20_long,
                          ifelse(stage %in% c("SG","D","G","X"),
                            stage,graz)) # Info that should be on "graz" column
ping_20_long$stage  <- with(ping_20_long,
                          ifelse(stage %in% c("SG","D","G","X"),
                            NA,stage))

unique(ping_20_long$stage) # Now correct info on "stage"
unique(ping_20_long$graz) # and on "graz"
```

# Create column for vegetative / flowering

```{r}
ping_17_long <- ping_17_long %>%
  mutate(V_F=ifelse(stage %in% c("V","B1","B2","B3","B4"),"V",
                    ifelse(stage %in% c("FL","FL100","W","W100"),"F",NA)))
```

```{r}
ping_18_long <- ping_18_long %>%
  mutate(V_F=ifelse(stage %in% c("V","B1","B2","B3","B4"),"V",
                    ifelse(stage %in% c("FL","FL100","W","W100"),"F",NA)))
```

```{r}
ping_20_long <- ping_20_long %>%
  mutate(V_F=ifelse(stage %in% c("V","B1","B2","B3","B4"),"V",
                    ifelse(stage %in% c("FL","FL100","W","W100"),"F",NA)))
```

# Calculate FFD (mean and corrected)

Get date for last recording with buds and first recording with flowers. Calculate FFD_meanDOY as the mean date between last recording with buds and first recording with flowers.

```{r message=FALSE, warning=FALSE}
# Calculate date when the plant was first recorded as flowering
date_firstF_17  <- ping_17_long %>%
  group_by(id) %>%
  filter(V_F=="F") %>%
  filter(date==min(date)) %>%
  mutate(date_firstF=date) %>%
  dplyr::select(id,date_firstF)

# Calculate date when the plant was last recorded as vegetative
# (before being recorded as flowering)
date_lastV_17  <- ping_17_long %>%
  group_by(id) %>%
  filter(V_F=="V") %>%
  full_join(date_firstF_17) %>%
  filter(date<=date_firstF) %>% 
  # Remove records after first record with flowers
  filter(date==max(date)) %>%
  mutate(date_lastV=date) %>%
  dplyr::select(id,date_lastV)

ping_17_FFD <- ping_17_long %>%
  dplyr::select(id,date,stage,V_F) %>%
  filter(!is.na(V_F)) %>%
  left_join(date_firstF_17) %>%
  filter(date<=date_firstF) %>% 
  # Remove records after first record with flowers
  left_join(date_lastV_17) %>%
  filter(date>=date_lastV|is.na(date_lastV)) %>%
  # Remove records before last record without flowers
  pivot_wider(id_cols=id,names_from=V_F,
              values_from=c(stage,date_firstF,date_lastV)) %>%
  dplyr::select(id,stage_V,stage_F,date_firstF_F,date_lastV_V) %>%
  rename(date_firstF=date_firstF_F,date_lastV=date_lastV_V) %>%
  ungroup() %>%
  arrange(id) %>%
  mutate(date_firstF=yday(date_firstF),date_lastV=yday(date_lastV)) %>%
  # Change to julian dates
  mutate(FFD_meanDOY=ifelse(is.na(date_lastV),date_firstF-3.9, 
                            # Calculate first estimate of FFD:
                            # For those flowering in first revision
                            # assigned FFD as half a mean interval
                            # date_firstF-(7.8/2)=date_firstF-3.9
                            (date_lastV+date_firstF)/2)) %>%
  # For others, assigned FFD_meanDOY as mean of date_lastV and date_firstF
  mutate(interval=date_firstF-date_lastV) %>%
  # Interval between 3 and 14 days (mean=7.8 days)
  mutate(term_lastV=ifelse(stage_V=="V"|stage_V=="B1",0.2*interval,
                    ifelse(stage_V=="B2",0*interval,
                    ifelse(stage_V=="B3"|stage_V=="B4",-0.2*interval,NA))),
         term_firstF=ifelse(stage_F=="FL"|stage_F=="FL100",0.2*interval,
                     ifelse(stage_F=="W"|stage_F=="W100",-0.2*interval,NA))) %>% 
  # Calculate terms to add for correcting FFD
  mutate(FFD_corr=ifelse(is.na(date_lastV),FFD_meanDOY-2.34, 
                         # Calculate corrected FFD:
  # For those flowering in first revision, stage_F is FL or FL100
  # FFD_corr is calculated as FFD_meanDOY-(7.8/2)+0.2*7.8 = FFD_meanDOY-2.34
  # (Supposing the mean duration of the interval 
  # and adding a term based on flowering stage)                        
                        FFD_meanDOY+term_lastV+term_firstF))
  # For others, FFD_cor is FFD_meanDOY + both terms
```

```{r message=FALSE, warning=FALSE}
# Calculate date when the plant was first recorded as flowering
date_firstF_18  <- ping_18_long %>%
  group_by(id) %>%
  filter(V_F=="F") %>%
  filter(date==min(date)) %>%
  mutate(date_firstF=date) %>%
  dplyr::select(id,date_firstF)

# Calculate date when the plant was last recorded as vegetative
# (before being recorded as flowering)
date_lastV_18  <- ping_18_long %>%
  group_by(id) %>%
  filter(V_F=="V") %>%
  full_join(date_firstF_18) %>%
  filter(date<=date_firstF) %>% 
  # Remove records after first record with flowers
  filter(date==max(date)) %>%
  mutate(date_lastV=date) %>%
  dplyr::select(id,date_lastV)

ping_18_FFD <- ping_18_long %>%
  dplyr::select(id,date,stage,V_F) %>%
  filter(!is.na(V_F)) %>%
  left_join(date_firstF_18) %>%
  filter(date<=date_firstF) %>% 
  # Remove records after first record with flowers
  left_join(date_lastV_18) %>%
  filter(date>=date_lastV|is.na(date_lastV)) %>%
  # Remove records before last record without flowers
  pivot_wider(id_cols=id,names_from=V_F,
              values_from=c(stage,date_firstF,date_lastV)) %>%
  dplyr::select(id,stage_V,stage_F,date_firstF_F,date_lastV_V) %>%
  rename(date_firstF=date_firstF_F,date_lastV=date_lastV_V) %>%
  ungroup() %>%
  arrange(id) %>%
  mutate(date_firstF=yday(date_firstF),date_lastV=yday(date_lastV)) %>%
  # Change to julian dates
  mutate(FFD_meanDOY=ifelse(is.na(date_lastV),date_firstF-3.6, 
                            # Calculate first estimate of FFD:
                            # For those flowering in first revision
                            # assigned FFD as half a mean interval
                            # date_firstF-(7.2/2)=date_firstF-3.6
                            (date_lastV+date_firstF)/2)) %>%
  # For others, assigned FFD_meanDOY as mean of date_lastV and date_firstF
  mutate(interval=date_firstF-date_lastV) %>%
  # Interval between 4 and 12 days (mean=7.2 days)
  mutate(term_lastV=ifelse(stage_V=="V"|stage_V=="B1",0.2*interval,
                    ifelse(stage_V=="B2",0*interval,
                    ifelse(stage_V=="B3"|stage_V=="B4",-0.2*interval,NA))),
         term_firstF=ifelse(stage_F=="FL"|stage_F=="FL100",0.2*interval,
                     ifelse(stage_F=="W"|stage_F=="W100",-0.2*interval,NA))) %>% 
  # Calculate terms to add for correcting FFD
  mutate(FFD_corr=ifelse(is.na(date_lastV),FFD_meanDOY-2.16, 
                         # Calculate corrected FFD:
  # For those flowering in first revision, stage_F is FL or FL100
  # FFD_corr is calculated as FFD_meanDOY-(7.2/2)+0.2*7.2 = FFD_meanDOY-2.16
  # (Supposing the mean duration of the interval 
  # and adding a term based on flowering stage)                        
                        FFD_meanDOY+term_lastV+term_firstF))
  # For others, FFD_cor is FFD_meanDOY + both terms
```

```{r message=FALSE, warning=FALSE}
# Calculate date when the plant was first recorded as flowering
date_firstF_20  <- ping_20_long %>%
  group_by(id) %>%
  filter(V_F=="F") %>%
  filter(date==min(date)) %>%
  mutate(date_firstF=date) %>%
  dplyr::select(id,date_firstF)

# Calculate date when the plant was last recorded as vegetative
# (before being recorded as flowering)
date_lastV_20  <- ping_20_long %>%
  group_by(id) %>%
  filter(V_F=="V") %>%
  full_join(date_firstF_20) %>%
  filter(date<=date_firstF) %>% 
  # Remove records after first record with flowers
  filter(date==max(date)) %>%
  mutate(date_lastV=date) %>%
  dplyr::select(id,date_lastV)

ping_20_FFD <- ping_20_long %>%
  dplyr::select(id,date,stage,V_F) %>%
  filter(!is.na(V_F)) %>%
  left_join(date_firstF_20) %>%
  filter(date<=date_firstF) %>% 
  # Remove records after first record with flowers
  left_join(date_lastV_20) %>%
  filter(date>=date_lastV|is.na(date_lastV)) %>%
  # Remove records before last record without flowers
  pivot_wider(id_cols=id,names_from=V_F,
              values_from=c(stage,date_firstF,date_lastV)) %>%
  dplyr::select(id,stage_V,stage_F,date_firstF_F,date_lastV_V) %>%
  rename(date_firstF=date_firstF_F,date_lastV=date_lastV_V) %>%
  ungroup() %>%
  arrange(id) %>%
  mutate(date_firstF=yday(date_firstF),date_lastV=yday(date_lastV)) %>%
  # Change to julian dates
  mutate(FFD_meanDOY=ifelse(is.na(date_lastV),date_firstF-3.7, 
                            # Calculate first estimate of FFD:
                            # For those flowering in first revision
                            # assigned FFD as half a mean interval
                            # date_firstF-(7.3/2)=date_firstF-3.7
                            (date_lastV+date_firstF)/2)) %>%
  # For others, assigned FFD_meanDOY as mean of date_lastV and date_firstF
  mutate(interval=date_firstF-date_lastV) %>%
  # Interval between 4 and 10 days (mean=7.3 days)
  mutate(term_lastV=ifelse(stage_V=="V"|stage_V=="B1",0.2*interval,
                    ifelse(stage_V=="B2",0*interval,
                    ifelse(stage_V=="B3"|stage_V=="B4",-0.2*interval,NA))),
         term_firstF=ifelse(stage_F=="FL"|stage_F=="FL100",0.2*interval,
                     ifelse(stage_F=="W"|stage_F=="W100",-0.2*interval,NA))) %>% 
  # Calculate terms to add for correcting FFD
  mutate(FFD_corr=ifelse(is.na(date_lastV),FFD_meanDOY-2.19, 
                         # Calculate corrected FFD:
  # For those flowering in first revision, stage_F is FL or FL100
  # FFD_corr is calculated as FFD_meanDOY-(7.3/2)+0.2*7.3 = FFD_meanDOY-2.19
  # (Supposing the mean duration of the interval 
  # and adding a term based on flowering stage)                        
                        FFD_meanDOY+term_lastV+term_firstF))
  # For others, FFD_cor is FFD_meanDOY + both terms
```

# Add info on peak

```{r}
ping_17_peak <- ping_17_peak %>% 
  mutate(plot=as.factor(Plot),id=Indv,date_peak=as.Date(Date,format="%d.%m.%y"),
         dm1=`Rosette dm1`,dm2=`Rosette dm2`,n_stems=`Nr. flowerstems`,
         max_h=`Max height`,med_h=`Median height`,comments_peak=Comments) %>%
  dplyr::select(-(Plot:Comments)) %>%
  mutate(n_stems=as.integer(ifelse(n_stems=="N/A",NA,n_stems)),
         max_h=as.numeric(ifelse(max_h=="N/A",NA,max_h)),
         med_h=as.numeric(ifelse(med_h=="N/A"|med_h=="missing",NA,med_h)))
```

```{r}
ping_18_peak <- ping_18_peak %>% 
  mutate(plot=as.factor(Plot),id=Indv,date_peak=as.Date(Date,format="%d.%m.%y"),
         dm1=`Rosette dm1`,dm2=`Rosette dm2`,n_stems=`Nr. flowerstems`,
         max_h=`Max height`,med_h=`Median height`,comments_peak=Comments) %>%
  dplyr::select(-(Plot:Comments)) %>%
  # Correct errors in max_h and med_h and make numeric vars
  mutate(max_h=str_remove(max_h,"\"")) %>%
  mutate(max_h=str_remove(max_h,"\"")) %>%
  mutate(med_h=str_remove(med_h,"\"")) %>%
  mutate(med_h=str_remove(med_h,"\"")) %>%
  mutate(max_h=as.numeric(ifelse(max_h=="N/A",NA,max_h))) %>%
  mutate(med_h=as.numeric(ifelse(med_h=="N/A",NA,med_h)))
```

```{r}
ping_20_peak <- ping_20_peak %>% 
  mutate(plot=as.factor(Plot),id=Indv.,
         F_NF=`F/NF/A (Flowering/Not Flowering/Aborted)`,
         date_peak=as.Date(Date,format="%d.%m.%y"),
         dm1=`Rosette 1`,dm2=`Rosette 2`,n_stems=`# stems`,
         h_stem1=`Stem 1`,h_stem2=`Stem 2`,h_stem3=`Stem 3`,h_stem4=`Stem 4`,
         h_stem5=`Stem 5`,n_seedpods=`Total fruits developed (end of season)`,
         n_seeds=`Total seeds`,comments_peak=`Comments on individual`,
         comments_seeds=`Comments on seedcounts`) %>%
  mutate(h_stem1=ifelse(h_stem1==60,6,h_stem1)) %>% # Correct wrong value
  dplyr::select(-(Plot:`Comments on seedcounts`)) %>%
  # Assign 0 seed pods to plants recorded as flowering with no info on seedpods
  mutate(n_seedpods=ifelse(F_NF=="F"&is.na(n_seedpods),0,n_seedpods)) %>%
  rowwise %>%
  mutate(max_h=ifelse(is.na(h_stem1),NA,max(c_across(h_stem1:h_stem5),
                                            na.rm=T))) %>%
  mutate(med_h=ifelse(is.na(h_stem1),NA,mean(c_across(h_stem1:h_stem5),
                                             na.rm=T))) %>%
  dplyr::select(-(h_stem1:h_stem5)) %>%
  dplyr::select(-F_NF)
```

# Add info on seedpods and seeds

```{r}
ping_17_seeds <- ping_17_seeds %>%
  mutate(plot=as.factor(Plot),id=`#`,n_seedpods=`Tot. sp`,
         coll_seedpods=`Coll. sp`,n_seeds=`n seeds`,
         comments_seeds=`Malin´s comments`) %>%
  dplyr::select(-(Plot:`Malin´s comments`))
nrow(filter(ping_17_seeds,n_seedpods!=coll_seedpods))
# Always collected all seedpods
```

```{r}
ping_17_seedpods <- ping_17_seedpods %>%
  mutate(id=`#`,F_NF=`F/NF (Flowering/Not Flowering)`,
         n_seedpods=`Total seedpods`) %>%
  dplyr::select(-(Plot:Comments)) %>%
  # Assign 0 seed pods to plants recorded as flowering with no info on seedpods
  mutate(n_seedpods=ifelse(F_NF=="F"&is.na(n_seedpods),0,n_seedpods))
```


```{r}
ping_18_seeds <- ping_18_seeds %>%
  mutate(plot=as.factor(Plot),id=`#`,
         n_seedpods=`Collected seedpods`, # Assuming this is true so far
         n_seeds=`Total seedcount`,comments_seeds=`Comments`) %>%
  dplyr::select(-(Plot:`Comments`)) %>%
  # Assign zero seeds to plants with zero seedpods
  mutate(n_seeds=ifelse(n_seedpods==0,0,n_seeds))
```

For 2020, info on seeds included in peak file.

# Merge all data

```{r}
ping_17_data <- left_join((ping_17_FFD %>% 
                             dplyr::select(id,FFD_corr)),
                          (ping_17 %>% 
                             dplyr::select(plot,id,x,y,peak,comments,temp)))%>%
  left_join(ping_17_peak) %>%
  left_join(ping_17_seedpods %>% dplyr::select (id,n_seedpods)) %>%
  left_join(ping_17_seeds %>% dplyr::select(plot,id,n_seeds,comments_seeds)) %>%
  # Assign zero seeds to plants with zero seedpods
  mutate(n_seeds=ifelse(n_seedpods==0,0,n_seeds)) %>%
  mutate(n_stems=ifelse(n_stems==21,2,n_stems)) # Fix error in n_stems
nrow(ping_17_data)
# 292 ids that flowered, 
nrow(ping_17_data %>% filter(peak==1))
# Of which 280 with info on peak
nrow(ping_17_data %>% filter(!is.na(n_seeds)))
# And 276 with info on seeds
```

```{r}
ping_18_data <- left_join((ping_18_FFD %>% 
                             dplyr::select(id,FFD_corr)),
                          (ping_18 %>% 
                             dplyr::select(plot,id,x,y,peak,comments,temp)))%>%
  left_join(ping_18_peak) %>%
  left_join(ping_18_seeds) 
nrow(ping_18_data)
# 201 ids that flowered, 
nrow(ping_18_data %>% filter(peak==1))
# Of which 201 with info on peak
nrow(ping_18_data %>% filter(!is.na(n_seeds)))
# And 199 with info on seeds
```

```{r}
ping_20_data <- left_join((ping_20_FFD %>% 
                             dplyr::select(id,FFD_corr)),
                          (ping_20 %>% 
                             dplyr::select(plot,id,x,y,peak,comments,start_treatment,
                                    treatment,temp)))%>%
  left_join(ping_20_peak) %>%
  # Assign zero seeds to plants with zero seedpods
  mutate(n_seeds=ifelse(n_seedpods==0,0,n_seeds)) %>%
  mutate(treatment=as.character(treatment)) %>%
  mutate(treatment=as.factor(ifelse(is.na(treatment),"C",treatment)))
nrow(ping_20_data)
# 287 ids that flowered, 
nrow(ping_20_data %>% filter(peak==1))
# Of which 284 with info on peak
nrow(ping_20_data %>% filter(!is.na(n_seeds)))
# And 279 with info on seeds
```

# Save clean data as .csv

```{r}
write_csv(ping_17_data,"data/clean/ping_17_data.csv")
write_csv(ping_18_data,"data/clean/ping_18_data.csv")
write_csv(ping_20_data,"data/clean/ping_20_data.csv")
```

```{r}
sessionInfo()
```

