---
title: "Response of Pinguicula vulgaris to geothermal heating"
subtitle: "Analyses"
author : "Alicia Valdés"
output:
  pdf_document:
    latex_engine: xelatex
    toc: yes
    toc_depth: 4
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
options(tibble.width = Inf)
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

```{r load packages, include=FALSE}
library(tidyverse)
library(readxl)
library(jtools)
library(RColorBrewer)
library(gridExtra)
library(ggeffects)
library(DHARMa)
```

```{r Define ggplot themes and palettes, include=FALSE}
my_theme <- function(){
  theme_base()+theme(plot.background=element_rect(fill="white", colour=NA))+
  theme(legend.position="none")+theme(text=element_text(family="serif"))+
  theme(plot.title = element_text(hjust =-0.06))
}
my_theme_legend <- function(){
  theme_base()+theme(plot.background=element_rect(fill="white", colour=NA))+
  theme(text=element_text(family="serif"))+
  theme(plot.title = element_text(hjust =-0.06))
}
myPalette <- colorRampPalette(brewer.pal(11, "YlOrRd"))
```

# Read clean data from .csv files

```{r}
ping_17_data <- read_csv("data/clean/ping_17_data.csv")
ping_18_data <- read_csv("data/clean/ping_18_data.csv")
ping_20_data <- read_csv("data/clean/ping_20_data.csv")
```

# Variable distributions

```{r}
grid.arrange(
  ggplot(ping_17_data,aes(x=FFD_corr))+geom_histogram()+my_theme()+ylab(NULL),
  ggplot(ping_18_data,aes(x=FFD_corr))+geom_histogram()+my_theme()+ylab(NULL),
  ggplot(ping_20_data,aes(x=FFD_corr))+geom_histogram()+my_theme()+ylab(NULL),
  ncol=3)
```

```{r}
grid.arrange(
  ggplot(ping_17_data,aes(x=temp))+geom_histogram()+my_theme()+ylab(NULL),
  ggplot(ping_18_data,aes(x=temp))+geom_histogram()+my_theme()+ylab(NULL),
  ggplot(ping_20_data,aes(x=temp))+geom_histogram()+my_theme()+ylab(NULL),
  ncol=3)
```

# 1. Effect of temperature on FFD

## Fit linear models

Not including number of flowers as covariate, including quadratic effects of ffd.

```{r echo=TRUE}
FFD_2017_1<-lm(FFD_corr~temp+I(temp^2),ping_17_data)
summ(FFD_2017_1,vif=T,scale=T) # scale=T reports standardized coefs
FFD_2018_1<-lm(FFD_corr~temp+I(temp^2),ping_18_data)
summ(FFD_2018_1,vif=T,scale=T) # scale=T reports standardized coefs
FFD_2020_1<-lm(FFD_corr~temp+I(temp^2),ping_20_data)
summ(FFD_2020_1,vif=T,scale=T) # scale=T reports standardized coefs
```

Quadratic effects significant in 2018 and 2020, but not on 2017.

Refit model for 2017 withouth quadratic term of ffd.

```{r echo=TRUE}
FFD_2017_2<-lm(FFD_corr~temp,ping_17_data)
summ(FFD_2017_2,scale=T)
```

## Model predictions

```{r}
plot(ggpredict(FFD_2017_2),add.data=T)
plot(ggpredict(FFD_2018_1),add.data=T)
plot(ggpredict(FFD_2020_1),add.data=T)
```

The effects look almost linear in 2018 and 2020.

Predictions of FFD_corr for minimum and maximum temperatures:

```{r}
ggpredict(FFD_2017_2,terms="temp[minmax]")
# 187.26-158.67=28.59 days earlier on warmer soils
ggpredict(FFD_2018_1,terms="temp[minmax]") 
# 196.72-154.57=42.15 days earlier on warmer soils
ggpredict(FFD_2020_1,terms="temp[minmax]") 
# 190.85-155.16=35.69 days earlier on warmer soils
```

## Model diagnostics

```{r}
simOutput_FFD_2017_2<-simulateResiduals(fittedModel=FFD_2017_2,
                                               n=5000)
simOutput_FFD_2018_1<-simulateResiduals(fittedModel=FFD_2018_1,
                                               n=5000)
simOutput_FFD_2020_1<-simulateResiduals(fittedModel=FFD_2020_1,
                                               n=5000)
```

```{r fig.height=4, fig.width=7}
plot(simOutput_FFD_2017_2)
plot(simOutput_FFD_2018_1)
plot(simOutput_FFD_2020_1)
```
















```{r}
sessionInfo()
```

